The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-07-03 VegOzone.tex
A few more lines for the abstract.

\begin{abstract}
  The summer 2018 and summer 2019 did not differ significantly in the level of ozone. On the other hand, the temperatures (precipitation and cloud cover/PAR?) differed quite a lot. We also observed ozone-induced visible injuries on clovers in the ozone garden at Svanhovd in 2018, but not in 2019. This may be due to differences in uptake of ozone ($\mathrm{POD_y}$) between the two years. Since DO3SE can be run on birch/beech and conifers, we would like to investigate whether the critical levels for these tree species were crossed during the two summer seasons. Ozone concentrations for the two missing weeks in July 2018 have been estimated based on the measurements from the Swedish and Finnish ozone measurement stations in the region.  
\end{abstract}

>>>>

\begin{abstract}
The past two decades saw a steady reduction in episodic high peak summer concentrations of ozone in Europe and North America thanks to the implementation of air quality regultions. At the same time, tropospheric background ozone levels have been increasing in general. The summer 2018 and summer 2019 did not differ significantly in the level of ozone. On the other hand, the temperatures (precipitation and cloud cover/PAR?) differed quite a lot. We also observed ozone-induced visible injuries on clovers in the ozone garden at Svanhovd in 2018, but not in 2019. This may be due to differences in uptake of ozone ($\mathrm{POD_y}$) between the two years. Since DO3SE can be run on birch/beech and conifers, we would like to investigate whether the critical levels for these tree species were crossed during the two summer seasons. Ozone concentrations for the two missing weeks in July 2018 have been estimated based on the measurements from the Swedish and Finnish ozone measurement stations in the region.  
\end{abstract}
